Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-18 doc/JFLA2022/paper.tex
thank the anonymous reviewers under acknowledgements

\section*{Acknowledgments}
\label{sect:acks}
We are grateful to the original authors and current maintainers of the Coq packages we use and depend on: José Grimm (Gaia), Russell O'Connor (Goedel), Matthieu Sozeau (Equations), the Mathematical Components team, Marc Lasson and Chantal Keller (Paramcoq), and the authors and maintainers of \coq and its associated tools.

>>>>

\section*{Acknowledgments}
\label{sect:acks}
We thank the anonymous reviewers for their comments, and we are grateful to the original authors and current maintainers of the Coq packages we use and depend on: José Grimm (Gaia), Russell O'Connor (Goedel), Matthieu Sozeau (Equations), the Mathematical Components team, Marc Lasson and Chantal Keller (Paramcoq), and the authors and maintainers of \coq and its associated tools.
